---
title: "Data Science Showcase - Unsupervised Learning"
author: "Shaun Latham, Glen Arch"
date: "2023-11-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(plotly)
library(ggpubr)
```

<h1>1. Introduction </h1>
Welcome to the Data Science Showcase, in this section we are detailing unsupervised learning and R.
<br></br>
Documentation relating to the decision making and time-management of the development of this code can be found <a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1/timeline?selectedIssue=DSS-1>here</a>. 

As part of the wider project, we had decided to demonstrate competency with unsupervised learning techniques and with R. 
The team therefore decided to find an example dataset then tidy and model it using R.

Actions within the team were tracked in the following issues:
<br></br>
Sprint <a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1?selectedIssue=DSS-8>DSS-8:</a> Create unsupervised learning model
<ul>
- <a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1?selectedIssue=DSS-15>DSS-15:</a> Find a compatible data-set (<a/href=https://github.com/Shaun-Latham>@ShaunLatham</a> <a/href=https://github.com/glen-arch>@GlenArch</a>)
- <a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1?selectedIssue=DSS-23>DSS-23:</a> Build & train model - K-means (<a/href=https://github.com/glen-arch>@GlenArch</a>)
- <a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1?selectedIssue=DSS-56>DSS-56:</a> Build & train model - principal component analysis (<a/href=https://github.com/Shaun-Latham>@ShaunLatham</a>)
- <a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1?selectedIssue=DSS-24>DSS-24:</a> Visualize the data & output of models (<a/href=https://github.com/Shaun-Latham>@ShaunLatham</a> <a/href=https://github.com/glen-arch>@GlenArch</a>)
</ul><br>





</br>
<h1>2. Exploring the data </h1>
<a/href=https://shaun-latham.atlassian.net/jira/software/projects/DSS/boards/1?selectedIssue=DSS-15>DSS-15:</a> Find a compatible dataset.
<br>
</br>
The team decided to utilize the iris dataset, which comes built into R.<br></br>
This dataset is a collection of measurements taken from individuals of three species of the <i>Iris</i> genus; <i>I. setosa</i>, <i>I. versicolor</i> and <i>I. virginica</i>, which are flowers.<br></br>
Below is a glimpse of the table and a summary of the population sizes and distributions:
```{r cars}
glimpse(iris)
summary(iris)
```
<br>
</br>
Firstly, it appears the variable names could use some tidying, the values are measured in cm but this is not reflected. The names are corrected below and saved to a new dataframe called 'data':
```{r}
data <- iris %>% 
  rename("Petal length (cm)" = Petal.Length,
         "Petal width (cm)" = Petal.Width,
         "Sepal length (cm)" = Sepal.Length,
         "Sepal width (cm)" = Sepal.Width)
glimpse(data)
```
<br></br>
Clearly, from looking at the tables alone, it is not easy to visualize how each species differs for these variables.<br></br>
Below are distribution plots examining each of the numeric variables:<br>
</br>
```{r}
subfig1 <-ggplot(data, aes(x=`Petal length (cm)`, group=Species, fill = Species)) +
geom_density(alpha=0.8)

subfig2<- ggplot(data, aes(x=`Petal width (cm)`, group=Species, fill = Species)) +
geom_density(alpha=0.8, show.legend=FALSE)

subfig3 <- ggplot(data, aes(x=`Sepal length (cm)`, group=Species, fill = Species)) +
geom_density(alpha=0.8, show.legend=FALSE)

subfig4 <- ggplot(data, aes(x=`Sepal width (cm)`, group=Species, fill = Species)) +
geom_density(alpha=0.8, show.legend=FALSE)

figure <- ggarrange(subfig1, subfig2, subfig3, subfig4,
                    labels = c("A", "B", "C", "D"),
                    ncol = 2, nrow = 2, 
                    common.legend = TRUE,
                    legend = "bottom")
annotate_figure(figure, top = text_grob("Figure 1: Density of flower dimensions by species",face="bold",size=14))

```